### 2025-03-13 paper/sections/other/main_results.qmd
uff

df = final_table(res_dir)
get_table_inputs(df, nothing; backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; table_type=:tabular, save_name="paper/tables/main.tex")
```

>>>>

df = final_table(res_dir)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(inputs; table_type=:tabular, save_name="paper/quarto_ecml/tables/main.tex", wrap_table=false)
tabulate_results(inputs; table_type=:tabular, save_name="paper/preprint/tables/main.tex", wrap_table=false)
```
